---
title: "Weekly Exercise 1: Welcome & R Fundamentals"
author: "Jiezi Yang"
format: html
---

<!--
HOW THIS WORKS
1. Answer each question by assigning your result to the object name given
   in the question (q1, q2, ...). Do not change the object names.
2. Render this document (the Render button in RStudio) to check that
   everything runs without error.
3. Commit and push your work to GitHub. Within 2 minutes, the Actions tab
   shows which questions pass. Revise and push freely before the deadline.
Reading: R02Pro Chapter 1 (https://r02pro.github.io/)
AI policy: AI tools allowed with the verify-then-use workflow. You must be
able to explain every line you submit.
-->

## Setup

Run this chunk first to load packages used in the questions.

```{r setup}
library(r02pro)
```

## Q1. R as a Calculator & Order of Operations (R02Pro 1.2)

In clinical medicine, Body Surface Area (BSA in $\text{m}^2$) is calculated using the Mosteller formula:

$$\text{BSA} = \sqrt{\frac{\text{height (cm)} \times \text{weight (kg)}}{3600}}$$

Calculate the BSA for an adult patient with a height of $178\text{ cm}$ and a weight of $82\text{ kg}$.
Assign the resulting numeric value to `q1`.

```{r q1}
q1 <- sqrt(178*82/3600) # replace NULL with your answer
```

## Q2. Object Assignment & Dynamic Variables (R02Pro 1.2)

A public health study plans to enroll participants with the following budget parameters:
- `n_participants <- 180`
- `cost_per_participant <- 375.50`
- `fixed_overhead <- 22000`

Assign these three variables, then calculate the total study budget:
$$\text{total budget} = \text{fixed overhead} + (\text{participants} \times \text{cost per participant})$$
Assign the total budget value to `q2`.

```{r q2}
q2 <- NULL # replace NULL with your answer
```

## Q3. Exponential Decay and Half-Life (R02Pro 1.2)

The plasma concentration $C(t)$ of an antibiotic follows first-order elimination:

$$C(t) = C_0 \times e^{-k \times t}$$

Given:
- Initial concentration $C_0 = 120\text{ mg/L}$
- Elimination rate constant $k = 0.18\text{ hr}^{-1}$
- Elapsed time $t = 8\text{ hours}$

Calculate the drug concentration at $t = 8$ using R's `exp()` function, and assign the result to `q3`.

```{r q3}
q3 <- NULL # replace NULL with your answer
```

## Q4. Function Arguments & Rounding (R02Pro 1.3)

Using your calculated value in `q3`, round the concentration to **2 decimal places**
using the `round()` function with the `digits` argument. Assign the rounded value to `q4`.

```{r q4}
q4 <- NULL # replace NULL with your answer
```

## Q5. Logarithmic Transformations (R02Pro 1.2)

In epidemiology and bioinformatics, data spanning multiple orders of magnitude are frequently transformed.
- The natural logarithm (base $e$) is computed with `log()`.
- The common logarithm (base $10$) is computed with `log10()`.

Given a viral load count of $450,000\text{ copies/mL}$:
Calculate the base-10 logarithm ($\log_{10}(450000)$) and assign the result to `q5`.

```{r q5}
q5 <- NULL # replace NULL with your answer
```

## Q6. Scientific Notation in R (R02Pro 1.2)

In large population health studies, numbers are often written in scientific notation.
For example, $1.5 \times 10^6$ is written in R as `1.5e6`.

A national health survey covers a population of $3.45 \times 10^7$ people.
If the disease incidence rate is $1.25 \times 10^{-4}$ per person-year,
calculate the expected number of incident cases per year:
$$\text{expected cases} = (3.45 \times 10^7) \times (1.25 \times 10^{-4})$$
Calculate this value directly in R using scientific notation (`e` syntax), and assign the result to `q6`.

```{r q6}
q6 <- NULL # replace NULL with your answer
```

## Q7. Multi-Step Unit Conversion & BMI (R02Pro 1.2)

A clinic records patient anthropometrics in imperial units:
- Weight: $165\text{ lbs}$ (where $1\text{ lb} = 0.45359237\text{ kg}$)
- Height: $68\text{ inches}$ (where $1\text{ inch} = 0.0254\text{ meters}$)

Calculate the patient's Body Mass Index ($\text{BMI} = \frac{\text{weight in kg}}{(\text{height in meters})^2}$),
and assign the resulting BMI value to `q7`.

```{r q7}
q7 <- NULL # replace NULL with your answer
```

## Q8. Package Functions & Absolute Differences (R02Pro 1.3, 1.4)

Make sure the `r02pro` package is loaded (`library(r02pro)`).
In the Ames housing dataset (`ahp` from `r02pro`), the first recorded sale price is $\$525,000$ and
the second recorded sale price is $\$480,000$.

Use the `abs()` function to compute the absolute difference between these two sale prices,
and assign the result to `q8`.

```{r q8}
q8 <- NULL # replace NULL with your answer
```
